Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-01 dissemination.publication/9375838469ad4029/paper.tex
added unified CK workflow

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unified installation and evaluation for the ReQuEST scoreboard using Collective Knowledge framework}

\subsubsection{Minimal CK installation}

The minimal installation requires:

\begin{packed_itemize}
 \item Python 2.7 or 3.3+ (limitation is mainly due to unitests)
 \item Git command line client.
\end{packed_itemize}

You can install CK in your local user space as follows:

\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

You can also install CK via PIP with sudo to avoid setting up environment variables yourself:

\begin{verbatim}
$ sudo pip install ck
\end{verbatim}

\subsubsection{CK repository installation}

\begin{verbatim}
$ ck pull repo:ck-request-asplos18-mobilenets-tvm-arm
\end{verbatim}

\subsubsection{PYNQ-Z1 FPGA installation (connected via RPC from host)}

Please follow this [getting started guide]() to set up your Pynq board.

We used pynq\_z1\_image\_2017\_02\_10.img with 16GB microSD card and Ubuntu 15.04.

Turn on your board. You should now be able to connect to it as follows:

\begin{verbatim}
$ ssh xilinx@192.168.2.99
\end{verbatim}

Use 'xilinx' as password (unless you changed it).

\textbf{Install global prerequisites (Ubuntu)}

Note that Ubuntu 15.04 is now outdated. You need to fix URLs of Ubuntu repos to be able to update it and install missing packages as follows:

\begin{verbatim}
$ sudo vim /etc/apt/sources.list.d/multistrap-wily.list
 deb [arch=armhf] http://old-releases.ubuntu.com/ubuntu wily universe main
 deb-src http://old-releases.ubuntu.com/ubuntu wily universe main
\end{verbatim}

Then you should be able to upgrade your distribution as follows:

\begin{verbatim}
$ sudo apt update
$ sudo apt upgrade
\end{verbatim}

Now you can install missing deps:

\begin{verbatim}
$ sudo apt install python-pip python3-pip
$ pip install wget
\end{verbatim}

\textbf{Install Collective Knowledge and this repository with all dependencies}

\begin{verbatim}
$ sudo pip install ck
$ ck pull repo:ck-request-asplos18-resnet-tvm-fpga
\end{verbatim}

\textbf{Install and run VTA RPC server via CK}

\begin{verbatim}

$ ck install package:lib-tvm-runtime-master --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c

  choose Python 3!

$ ck run program:vta-pynq-server --sudo

  during first execution other missing soft dependencies will be detected or installed including libdma.so and VTA server

\end{verbatim}

If libdma.so is installed in an unusual directory and was not automatically found by CK, 
you can register it manually as follows (and then restart above commands):

\begin{verbatim}
$ ck detect soft:lib.pynq.dma --search_dirs={path to libdma.so)
\end{verbatim}

Note that by default this server will run on host '192.168.2.99' and port '9091'.

Now you can configure your host machine to classify images via this board.

\subsubsection{Installation: host machine (tested on Ubuntu or similar)}

Install missing deps:

\begin{verbatim}
$ sudo apt install python-pip python3-pip
$ pip install wget
\end{verbatim}

\textbf{Install Collective Knowledge and this repository with all dependencies}

\begin{verbatim}
$ sudo pip install ck
$ ck pull repo:ck-request-asplos18-resnet-tvm-fpga
\end{verbatim}

\textbf{Install TVM, NNVM and VTA}

\begin{verbatim}
$ ck install package:lib-tvm-master-cpu --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
 Select Python 2.x
 LLVM > 4.x

$ ck install package:lib-nnvm-master --env.PACKAGE_URL=https://github.com/tqchen/nnvm --env.PACKAGE_GIT_CHECKOUT=qt

$ ck install package:lib-vta-python-master
\end{verbatim}

\textbf{Set up RPC access to VTA server}

\begin{verbatim}
$ ck add machine:pynq
\end{verbatim}

Select "remote machine accessed via RPC", then enter hostname and port.

You can then check if VTA server running as follows:

\begin{verbatim}
$ ck show machine
\end{verbatim}

\textbf{Run classification}

You can now try to classify some image via VTA server as follows:

\begin{verbatim}
$ ck run program:request-tvm-vta-pynq --cmd_key=classify --target=pynq
\end{verbatim}

\textbf{Test accuracy}

Finally, you can test accuracy on IMAGENET as follows:

\begin{verbatim}
$ ck run program:request-tvm-vta-pynq --cmd_key=test target=pynq
\end{verbatim}

Note that if board crahes, you can restart above program and it will continue aggregating statistics
via "program/request-tvm-vta-pynq/tmp/aggregate-ck-timer.json" file. 
You can delete it if you want to collect "fresh" stats.

\textbf{Run benchmarking in a unified ReQuEST way and record results}

You can run performance benchmark and record experiments as follows:

\begin{verbatim}
$ cd `ck find script:benchmark-request-tvm-fpga`
$ python benchmarking.py
\end{verbatim}

Your results will be recorded in local:experiment:ck-request-asplos18-tvm-fpga-performance-* entries:
\begin{verbatim}
$ ck ls local:experiment:ck-request-asplos18-tvm-fpga-performance-*
\end{verbatim}

You can pack them and send to ReQuEST organizers as follows:

\begin{verbatim}
$ ck zip local:experiment:ck-request-asplos18-tvm-fpga-performance-*
\end{verbatim}
